Decomposing labelled proof theory for~intuitionistic~modal~logic

### 2020-08-25 FullyLabelled/JLC/reviews/notes.tex
adding TODO

\documentclass[11pt]{article}

@@

\end{itemize}

\begin{proposition}

	The rules $\llabrn{cont}$ and $\rlabrn{cont}$ are admissible for $\labIKp$.
	\begin{center}
		$\vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}$\quad\quad$\vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}$
	\end{center}
\end{proposition}
\begin{proof}
	The rule $\llabrn{cont}$ can be derived using $\rn{refl}$ and $\llabrn{mon}$ which is admissible by Proposition 3.1.

@@

$$
	\vlderivation{
		\vlin{\rlabrn\BOX}{}{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}{
			\vlin{\rlabrn\IMP}{\lb v\mbox{ fresh}}{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}{
				\vlin{\rn F_1}{\lb u\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
					\vlin{\rn g_{1110}}{ \lb{w}\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
							\vlin{\llabrn\BOX}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
								\vlin{\rn{id}}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A}, \labels{v}{A} \SEQ \labels{v}{A}}{
									\vlhy{}
							}
						}
					}
				}
			}
		}
	}
$$

@@

\begin{itemize}
	\item \emph{Broken references “??” in pages 13 and 14}: {\color{green}Fixed.}
	\item \emph{The section of ``Extensions" has to be more detailed:
		\begin{itemize}
			\item it does not help at all that the
			applications of the rule g1111 are merged with $\llabrn\BOX$ and $\rlabrn\DIA$ in the example
			derivation. {\color{green}Fixed.}
			\item Most importantly, I am not convinced by the gklmn rule. The side condition stipulates that $\lb y'$ and $\lb u$ are fresh, whereas the frame property contains existential quantifications. I was thus expecting either a Skolemization in the style of Vigano in the ``Labelled Non-Classical Logics" book, or a geometric rule with existential quantification in the style of Simpson [Sim94] or, perhaps even better, a “mixed” rule where the labels are	assumed more or less in the style of an $\exists$ elimination to derive a labeled formula.
		\end{itemize}}
	\item \emph{Remark 4.2. Show the ``need" you would likely have to show that no other proofs of the axioms are possible. That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.}:

	There are two options: 
	1. Do not use the word ``need'';
	2. Show that no other proofs of the axioms are possible.

	\item \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
\end{itemize}

>>>>

\documentclass[11pt]{article}
\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}

@@

\end{itemize}
\todo{Add next remark to the paper with a small explanation:}
\begin{remark}

	The rules $\llabrn{cont}$ and $\rlabrn{cont}$ are admissible for $\labIKp$.
	\begin{center}
		$\vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}$\quad\quad$\vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}$
	\end{center}
\end{remark}
\begin{proof}
	The rule $\llabrn{cont}$ can be derived using $\rn{refl}$ and $\llabrn{mon}$ which is admissible by Proposition 3.1.

@@

\todo{Add next proof as an example and a paragraph explaning.}
$$
	\vlderivation{
		\vlin{\rlabrn\BOX}{}{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}{
			\vlin{\rlabrn\IMP}{\lb v\mbox{ fresh}}{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}{
				\vlin{\rn F_1}{\lb u\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
					\vlin{\rn g_{1110}}{ \lb{w}\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
							\vlin{\llabrn\BOX}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
								\vlin{\rn{id}}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A}, \labels{v}{A} \SEQ \labels{v}{A}}{
									\vlhy{}
							}
						}
					}
				}
			}
		}
	}
$$

\begin{itemize}
	\item \emph{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in
	detail, as otherwise the authors’ work would rather look a routine exercise.}: \todo{add a paragraph about constructive modal logics.}
	\item \todo{Add a paragraph with all the references we are missing.}
\end{itemize}

@@

\begin{itemize}
	\item \emph{Broken references “??” in pages 13 and 14}: {\color{green}Fixed.}
	\item \emph{The section of ``Extensions" has to be more detailed:
		\begin{itemize}
			\item it does not help at all that the
			applications of the rule g1111 are merged with $\llabrn\BOX$ and $\rlabrn\DIA$ in the example
			derivation. {\color{green}Fixed.}
			\item Most importantly, I am not convinced by the gklmn rule. The side condition stipulates that $\lb y'$ and $\lb u$ are fresh, whereas the frame property contains existential quantifications. I was thus expecting either a Skolemization in the style of Vigano in the ``Labelled Non-Classical Logics" book, or a geometric rule with existential quantification in the style of Simpson [Sim94] or, perhaps even better, a “mixed” rule where the labels are	assumed more or less in the style of an $\exists$ elimination to derive a labeled formula. \todo{}
		\end{itemize}}
	\item \emph{Remark 4.2. Show the ``need" you would likely have to show that no other proofs of the axioms are possible. That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.}:

	There are two options: 
	\todo{Do not use the word ``need''.}

	\item \todo{LUTZ: \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}}
\end{itemize}
